Towards Ecosystem Management from Greedy Reinforcement Learning in a Predator-Prey Setting

### 2021-01-05 paper/paper.tex
Recompile paper with new figures

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=8cm]{figures/fish_pop_chart3.png}
\caption{Left-over fish population per learning episode over 12M steps}
\label{fig:fish_pop}
\end{center}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=6cm]{figures/shark_speeds.png}
\caption{Distribution of shark speeds over time}
\label{fig:shark_speeds}
\end{center}
\end{figure}

\blindtext[8]

>>>>

\blindtext[5]

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=8cm]{figures/dqncomp1fish_2.png}
\caption{Sustainability of static, static-wait, DQN Stage II and PPO with initial fish population of 1.}
\label{fig:dqncomp1}
\end{center}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=8cm]{figures/dqncomp2fish_2.png}
\caption{Sustainability of static, static-wait, DQN Stage II and PPO with initial fish population of 2.}
\label{fig:dqncomp2}
\end{center}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=8cm]{figures/fish_pop_chart3.png}
\caption{Left-over fish population per learning episode over 12M steps.}
\label{fig:fish_pop}
\end{center}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=6cm]{figures/shark_speeds.png}
\caption{Distribution of shark speeds over time.}
\label{fig:shark_speeds}
\end{center}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=8cm]{figures/Sterberisiko_vs_Herding_Two_Net_2.png}
\caption{TODO : Placeholder Chart (Idea: Three distributions with fish pop i10,i5,i2)}
\label{fig:herding}
\end{center}
\end{figure}

\begin{figure*}[t]
\begin{center}
\includegraphics[width=\textwidth]{figures/coop_movie_frames2.png}
\caption{From left to right: Two sharks cooperatively catch a fish.}
\label{fig:coop_movie}
\end{center}
\end{figure*}

\begin{figure*}%
    \centering
    \subfloat[][\centering Cooperation rate with initial fish population of 10.]{\includegraphics[width=5.5cm]{figures/coop_chart_split1.png} }%
    \subfloat[][\centering Cooperation rate with initial fish population of 5.]{\includegraphics[width=5.5cm]{figures/coop_chart_split2.png} }%
    \subfloat[][\centering Cooperation rate with initial fish population of 5 and stuns.]{\includegraphics[width=6.5cm]{figures/coop_chart_stuns_split2.png} }%
    \caption{Cooperation rate in different scenarios.}%
    \label{fig:coop}%
\end{figure*}

\begin{figure*}[t]
\begin{center}
\includegraphics[width=14cm]{figures/coop_vs_sterberisiko_5fish.png}
\caption{Cooperation rate vs starving pressure with initial fish population of 5.}
\label{fig:coop_starve}
\end{center}
\end{figure*}

\blindtext[14]
